---
title: "hw6"
author: "Kexin Sun"
date: "12/8/2020"
output: github_document
---


```{r}

library(tidyverse)
library(readxl)
library(patchwork)
library(ggplot2)
library(modelr)
library(p8105.datasets)
library(mgcv)

knitr::opts_chunk$set(
  fig.height = 6,
  fig.width = 8,
  message = F,
  echo = T,
  warning = F
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 2

Load the data

```{r}
birthweight =
  read_csv(here::here("data/birthweight.csv")) %>%
  janitor::clean_names() %>%
  mutate(
    across(
      c("frace", "mrace"),
      ~ case_when(
        .x == 1 ~ "White",
        .x == 2 ~ "Black",
        .x == 3 ~ "Asian",
        .x == 4 ~ "Puero Rican",
        .x == 8 ~ "Other",
        .x == 9 ~ "Unknown"
      )
    ),
    across(where(is.character), as.factor),
    malform = case_when(malform == 0 ~ "absent",
                        malform == 1 ~ "present"),
    malform = as.factor(malform),
    babysex = case_when(babysex == 1 ~ "male",
                        babysex == 2 ~ "female") %>% as.factor()
  )
birthweight %>% skimr::skim_without_charts()
```


Fit the model. `babysexmale`, `bhead`, `blength`, `delwt`, `gaweeks` and `wtgain` are predictors.  
```{r}
model_df =
  birthweight %>%
  select(bwt, babysex, bhead, blength, delwt, gaweeks, wtgain)

mul_model = lm(bwt ~ ., data = model_df)
summary(mul_model)
```

```{r}
step(mul_model, direction = "backward")
```

Model 1 
```{r}
model1 <- lm(bwt ~ ., data = model_df)
summary(model1)
model1 %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable()
```

```{r}
model_df =
  model_df %>% 
  modelr::add_predictions(model1) %>% 
  modelr::add_residuals(model1)
model_df
```

Most dots are distributed around 0, but there are also some outliers.
```{r}
model_df %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  labs(
    title = "Predictors vs. Residuals Plot",
    x = "Predictors",
    y = "Residuals"
  )
```

The density plot follows a normal distribution and centered around 0.
```{r}
model_df %>% 
  ggplot(aes(x = resid)) +
  geom_density() +
  labs(
    title = "Residuals plot",
    x = "Residuals",
    y = "Density"
  )
```


Create other two models
```{r}
model2 =
  lm(bwt ~ blength + gaweeks, data = birthweight)
summary(model2)

model2 %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable()
```

```{r}
model3 =
  lm(bwt ~ babysex * bhead * blength, data = birthweight)
summary(model3)

model3 %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable()
```

Cross Validation
```{r}
cv =
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
cv_birthweight =
  cv %>% 
    mutate(
        model1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + wtgain, data = .x)),
        model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
        model3 = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
    ) %>% 
    mutate(
        rmse1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
        rmse2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
        rmse3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y))
    )
```


As we can see, Model1 has the lowest RMSE, which indicates that it fits the data best. 
```{r}
cv_birthweight %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin() +
  labs(
    title = "Comparison Between Three Models",
    x = "Model",
    y = "rmse"
  )
```

## Problem 3

```{r}

weather_df =
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"),
    date_min = "2017-01-01",
    date_max = "2017-12-31"
  ) %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10
  ) %>%
  select(name, id, everything())
```

Get the distribution plot:

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm")
```


Bootstrap:

```{r}
set.seed(1)
weather_bootstrap =
  modelr::bootstrap(weather_df,
                    n = 5000,
                    id = "id") %>%
  mutate(
    strap = map(strap, as_tibble),
    md =
      map(.x = strap,
          ~ lm(tmax ~ tmin, data = .x)),
    r_square =
      map2_dbl(.x = md,
               .y = strap,
               ~ modelr::rsquare(.x, .y)),
    md = map(md, broom::tidy)
  ) %>%
  unnest(md) %>%
  select(id, term, estimate, std_error = std.error, r_square)

weather_bootstrap %>% head() %>% knitr::kable()
```


The 95% confidence interval of r̂ squared and  log(β̂ 0∗ β̂ 1).


```{r boostrap_result}
weather_bootstrap %>%
  distinct(id, r_square) %>%
  summarise(lower = quantile(r_square, 0.025),
            upper = quantile(r_square, 0.975)) %>%
  knitr::kable()

weather_bootstrap %>%
  select(id, term, estimate) %>%
  pivot_wider(names_from = term,
              values_from = estimate
              ) %>%
  janitor::clean_names() %>%
  mutate(log_beta =log(tmin * intercept)) %>%
  summarise(lower = quantile(log_beta, 0.025),
            upper = quantile(log_beta, 0.975)
            ) %>%
  knitr::kable()

```
The 95% confidence interval for r̂ squared is (0.894, 0.927)

The 95% confidence interval for log(Beta1*Beta2) is (1.97, 2.06)



The distribution plot:

```{r}
weather_bootstrap %>%
  distinct(id, r_square) %>%
  ggplot(aes(x = r_square)) +
  geom_density()+
  labs(
    title = "Distribution of R^2"
  )
weather_bootstrap %>%
  select(id, term, estimate) %>%
  pivot_wider(names_from = term,
              values_from = estimate) %>%
  janitor::clean_names() %>%
  mutate(log_beta =
           log(tmin * intercept)) %>%
  ggplot(aes(x = log_beta)) +
  geom_density() +
  labs(
    title = "Distribution of log( β̂ 0∗β̂1)"
  )
```



The distribution of r̂ squared is approximately normal and follows the Central Limit Theroem. The distribution centered around 0.915
 
The distribution of log(beta0hat and the beta1hat) is approximately normal and follows the Central Limit Theroem. The distribution centered around 2.02



